Poster figures

### 2025-02-27 analysis/poster_ncar/presentation_figures.Rmd
More delta tweaks
Changes breaks in lon_rmse plots

```{r extent-delta, fig.height=11.99/cm, fig.width=24.45/cm}

@@

```{r fig-bias}
#| fig-cap: Mean sea ice concentrations 1-month lag monthly mean +S2 forecast bias compared with NSIDC.

bias_plot <- function(hindcast_clim, which_version, which_lead) {
  hindcast_clim |> 
    _[version == which_version] |>
    _[month_diff == which_lead] |> 
    # dcast(time + xgrid + ygrid ~ model, value.var = "aice") |> 
    # setnames(which_dataset, "obs") |>
    ggplot(aes(xgrid, ygrid)) +
    geom_contour_fill(aes(z = aice - obs, fill = after_stat(level)), 
                      breaks = AnchorBreaks(binwidth = 0.1, exclude = 0)) +
    # geom_contour2(aes(z = aice - obs), breaks = AnchorBreaks(binwidth = 0.1, exclude = 0),
    #               linewidth = 0.1) +
    scale_fill_divergent_discretised(paste0(which_version, " bias at ", which_lead, " months at lead time"),
                                     low = trans_pink,
                                     high = trans_blue) +
    geomcoord_antarctica +
    geom_antarctica_fill +
    facet_wrap(~ month, 
               labeller = labeller(month = setNames(months, month.abb)),
               nrow = 2) +
    wide_legend +
    tag_facets()
}

@@

```{r bias_S2_0, fig.width=width_bias, fig.height=height_bias}
hindcast_clim |> 
  bias_plot("S2", 0)
```

```{r bias_S1_0, fig.width=width_bias, fig.height=height_bias}
hindcast_clim |> 
  bias_plot("S1", 0)
```

lead
```{r bias_S2_6, fig.width=width_bias, fig.height=height_bias}
hindcast_clim |> 
  bias_plot("S2", 6)

@@

```{r bias_S1_6, fig.width=width_bias, fig.height=height_bias}
hindcast_clim |> 
  bias_plot("S1", 6)
```

>>>>

```{r extent-delta, fig.height=11.99/cm, fig.width=24.09/cm}

@@

```{r bias_plot}
#| fig-cap: Mean sea ice concentrations 1-month lag monthly mean +S2 forecast bias compared with NSIDC.

bias_plot <- function(hindcast_clim, which_version, which_lead) {

  breaks <- seq(-1, 1, by = 0.1)
  breaks <- breaks[breaks != 0]
  hindcast_clim |> 
    _[version == which_version] |>
    _[month_diff == which_lead] |> 
    # dcast(time + xgrid + ygrid ~ model, value.var = "aice") |> 
    # setnames(which_dataset, "obs") |>
    ggplot(aes(xgrid, ygrid)) +
    geom_contour_fill(aes(z = aice - obs, fill = after_stat(level)), 
                      breaks = breaks) +
    # geom_contour2(aes(z = aice - obs), breaks = AnchorBreaks(binwidth = 0.1, exclude = 0),
    #               linewidth = 0.1) +
    scale_fill_divergent_discretised(paste0(which_version, " bias at ", which_lead, " months at lead time"),
                                     low = trans_pink,
                                     high = trans_blue) +
    geomcoord_antarctica +
    geom_antarctica_fill +
    facet_wrap(~ month, 
               labeller = labeller(month = setNames(months, month.abb)),
               nrow = 2) +
    wide_legend +
    tag_facets()
}

@@

```{r bias_S2_0, fig.width=width_bias, fig.height=height_bias, dependson="bias_plot"}

hindcast_clim |> 
  bias_plot("S2", 0)
```

```{r bias_S1_0, fig.width=width_bias, fig.height=height_bias, dependson="bias_plot"}

hindcast_clim |> 
  bias_plot("S1", 0)
```

lead
```{r bias_S2_6, fig.width=width_bias, fig.height=height_bias, dependson="bias_plot"}
hindcast_clim |> 
  bias_plot("S2", 6)

@@

```{r bias_S1_6, fig.width=width_bias, fig.height=height_bias, dependson="bias_plot"}
hindcast_clim |> 
  bias_plot("S1", 6)
